---
title: "Vignette for eplR"
author: "Gerald Lee"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{eplR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(eplR)
```

***

### Data that comes with the package

The `eplR` package comes with a built in dataset for 17 seasons of English Premier League (soccer) games. They are from 2002/2003 to 2018/2019. To call on the dataset just use call `eplData`. The format of `eplData` is a list of dataframes so to get the dataframe for 2009/2010 season use the following code:

```{r}
# Get Data for season 2009/2010
head(eplData[[8]])
```

***

### Specific Data Query

For an easier version to query the data. You can use the `getData()` function. This function allows you to specify the season, whether you want additional betting information and whether you only want to have season data for a specific team.

```{r}
# Query Data
head(getData(1617, bet = FALSE, team = "Liverpool"))
```

***

### Referee Data

For users who are interested in analysing the season statistics for referees, you can use the `referee()` function, which will output a specialized query for referee-related information.

```{r}
# Get Referee stats for 2013-2014 season
head(referee(1314))
```

***

### Team Data

To get summary statistics for a particular team during a particular season, use the `teamData()` function.

```{r}
teamData(1112, "Wolves")
```

***

### Team Performance

To visualize the performance of a team over the course of a particular season, use the `teamPerformance()` function.

```{r}
# Look at the performance of Man City and Man United in the 2018-2019 season
teamPerformance(1819, "Man City")
teamPerformance(1819, "Man United")
```

